Bootstrap Confidence Intervals for Regression Discontinuity Designs with Uniform Kernels

### 2016-02-26 main_paper.tex
Update simulation tables

The functional form for $\mu_{1}(x)$ and $\mu_{2}(x)$ follow the data observed by \cite{lee2008} and \cite{ludwig2007}, respectively, while $\mu_{3}(x)$ is a transformation of $\mu_{1}(x)$ designed to emphasize its curvature and therefore bias in the usual RD approach. For the simulation studies, we used 250 bootstraps for bias correction, 999 bootstraps to calculate confidence interval and a total 500 replications. All results presented are based on a 0.95 desired confidence level. Table1 presents the main results in which a local-linear RD estimator ($p=1$) is employed with the bias-correction based on a local-quadratic approximation ($q=2$). Table 2 presents similar results for $p=2$ and $q=3$.

\begin{table}[t] \label{Tb1}
\centering
\begin{tabular}{rrrrrrrrr}
  \toprule
  DGP & Method    & Bias    & SD    & MSE   & CI coverage & CI length \\
  \midrule
  1   & bootstrap & --0.013 & 0.067 & 0.068 & 0.938       & 0.243     \\
      & CCT       & --0.016 & 0.068 & 0.070 & 0.908       & 0.244     \\
  2   & bootstrap & --0.014 & 0.083 & 0.084 & 0.954       & 0.319     \\
      & CCT       & --0.014 & 0.092 & 0.093 & 0.928       & 0.350     \\
  3   & bootstrap & --0.006 & 0.069 & 0.070 & 0.956       & 0.247     \\
      & CCT       & --0.004 & 0.071 & 0.071 & 0.918       & 0.249     \\
  \bottomrule
\end{tabular}
\caption{Summary of estimates ($p = 1, q = 2$)}
\end{table}

As can be seen on the tables above, the bootstrap bias-correction procedure
proposed in this paper provides a simple alternative to obtain valid robust
confidence intervals in RD designs and performs well compared to the analytical 
bias correction procedures proposed by CCT.

\begin{table}[t]\label{Tb2}
\centering
\begin{tabular}{rrrrrrr}
  \toprule
  DGP & Method    & Bias    & SD    & MSE   & CI coverage & CI length \\
  \midrule
  1   & bootstrap & --0.002 & 0.075 & 0.075 & 0.958       & 0.295     \\
      & CCT       & --0.004 & 0.082 & 0.082 & 0.926       & 0.295     \\
  2   & bootstrap & 0.002   & 0.087 & 0.086 & 0.934       & 0.302     \\
      & CCT       & --0.005 & 0.078 & 0.078 & 0.960       & 0.323     \\
  3   & bootstrap & --0.008 & 0.083 & 0.083 & 0.942       & 0.292     \\
      & CCT       & --0.003 & 0.080 & 0.080 & 0.938       & 0.295     \\
  \bottomrule
\end{tabular}
\caption{Summary of estimates from bootstrap ($p = 2, q = 3$)}
\end{table}

>>>>

The functional form for $\mu_{1}(x)$ and $\mu_{2}(x)$ follow the data observed by \cite{lee2008} and \cite{ludwig2007}, respectively, while $\mu_{3}(x)$ is a transformation of $\mu_{1}(x)$ designed to emphasize its curvature and therefore bias in the usual RD approach. For each DGP, we used four methods to obtain point estimate and 0.95 confidence interval. For each method, a total 1500 replications were performed. The first two methods follow CCT procedure with triangular and uniform kernel. The third and fourth methods follow the bootstrap procedure with uniform kernel. The only difference between the last two is that one is bias corrected and the other is not. In the bootstrap procedure, we used 500 bootstraps for bias correction, 999 bootstraps to calculate confidence interval. Table \ref{Tb: simulation 1} presents the main results in which a local-linear RD estimator ($p=1$) is employed with the bias-correction based on a local-quadratic approximation ($q=2$). Table \ref{Tb: simulation 2} presents similar results for $p=2$ and $q=3$.

\begin{table}[t]
\centering
\begin{tabular}{rrrrrrrrr}
  \toprule
	DGP & Method    & Bias    & SD    & MSE   & CI coverage & CI length \\
  \midrule
	1 & $CCT_{tri}$ & -0.010 & 0.068 & 0.068 & 0.911 & 0.241 \\ 
	  & $CCT_{uni}$ & -0.016 & 0.067 & 0.069 & 0.924 & 0.246 \\ 
	  & $bootstrap_{uni}$       & -0.018 & 0.066 & 0.069 & 0.931 & 0.240 \\ 
	  & $bootstrap_{uni}^{nbc}$ & -0.020 & 0.060 & 0.064 & 0.916 & 0.208 \\
	\midrule
	2 & $CCT_{tri}$ & -0.011 & 0.085 & 0.086 & 0.935 & 0.343 \\ 
	  & $CCT_{uni}$ & -0.010 & 0.087 & 0.088 & 0.938 & 0.350 \\ 
	  & $bootstrap_{uni}$       & -0.012 & 0.088 & 0.089 & 0.953 & 0.324 \\ 
	  & $bootstrap_{uni}^{nbc}$ & -0.051 & 0.086 & 0.100 & 0.869 & 0.300 \\ 
	\midrule
	3 & $CCT_{tri}$ & -0.008 & 0.067 & 0.067 & 0.919 & 0.246 \\ 
	  & $CCT_{uni}$ & -0.004 & 0.065 & 0.065 & 0.943 & 0.250 \\ 
	  & $bootstrap_{uni}$       & -0.004 & 0.064 & 0.064 & 0.960 & 0.246 \\ 
	  & $bootstrap_{uni}^{nbc}$ & 0.016 & 0.062 & 0.064 & 0.931 & 0.218 \\ 
  \bottomrule
\end{tabular}
\caption{Summary of estimates ($p = 1, q = 2$)}
\label{Tb: simulation 1}
\end{table}

As can be seen on the tables, the bootstrap bias-correction procedure proposed in this paper provides a simple alternative to obtain 
valid robust confidence intervals in RD designs and performs well compared to the analytical 
bias correction procedures proposed by CCT. The results also demonstrate the importance of bias correction when huge kink 
presents at the cutoff (such as in the second DGP). Failing to correct bias in this case leads to a confidence interval with incorrect coverage.

\begin{table}[t]
\centering
\begin{tabular}{rrrrrrr}
  \toprule
  DGP & Method    & Bias    & SD    & MSE   & CI coverage & CI length \\
  \midrule
    1 & $CCT_{tri}$ & -0.006 & 0.079 & 0.079 & 0.923 & 0.291 \\ 
      & $CCT_{uni}$ & -0.003 & 0.081 & 0.081 & 0.932 & 0.299 \\ 
      & $bootstrap_{uni}$       & -0.003 & 0.079 & 0.079 & 0.947 & 0.294 \\ 
      & $bootstrap_{uni}^{nbc}$ & -0.008 & 0.073 & 0.074 & 0.941 & 0.261 \\ 
     \midrule
    2 & $CCT_{tri}$ & -0.007 & 0.080 & 0.080 & 0.941 & 0.319 \\ 
      & $CCT_{uni}$ & -0.005 & 0.081 & 0.081 & 0.946 & 0.326 \\ 
      & $bootstrap_{uni}$       & -0.008 & 0.080 & 0.080 & 0.955 & 0.300 \\ 
      & $bootstrap_{uni}^{nbc}$ & -0.020 & 0.075 & 0.078 & 0.924 & 0.273 \\ 
     \midrule
    3 & $CCT_{tri}$ & 0.004 & 0.080 & 0.080 & 0.922 & 0.291 \\ 
      & $CCT_{uni}$ & -0.004 & 0.082 & 0.082 & 0.931 & 0.296 \\ 
      & $bootstrap_{uni}$       & 0.002 & 0.077 & 0.077 & 0.958 & 0.294 \\ 
      & $bootstrap_{uni}^{nbc}$ & -0.001 & 0.073 & 0.073 & 0.948 & 0.260 \\ 
  \bottomrule
\end{tabular}
\caption{Summary of estimates from bootstrap ($p = 2, q = 3$)}
\label{Tb: simulation 2}
\end{table}
